Contextual Combinatorial Cascading Bandits

### 2015-12-06 contextual combinatorial cascading bandits.tex
add comment

\wei{I do not see the purpose of putting Lemma 4.4 and 4.5 in this section. Perhaps
	they should all be moved to Section 4.3}

@@

\wei{I do not understand the above paragraph and the formula below.}
\begin{align*}
&~~\EE_t[R(t, \bA_t)] \\
&= \EE_t[R(t, \bA_t)(1/p_{t, \bA_t}) \bOne\{R(t, \bA_t) > 0, \bO_t \geq \abs{\bA_t}\}],\\
&~~\EE_t[R_{\wedge}(t, \bA_t)] \\
&= \EE_t[R_{\wedge}(t, \bA_t)(1/p_{\wedge, t, \bA_t}) \bOne\{R_{\wedge}(t, \bA_t) > 0, \bO_{\wedge, t} \geq \abs{\bA_t}\}].
\end{align*}

@@

The following lemma provides the relationship between an estimated mean vector and its
	upper bound, in terms of their $f$ function values.
\wei{The symbol here may need to be changed. $w_i$ coincides with weight $w_i$ before, 
		and $p$ coincides with many related probability definition using $p$.
	$w_i$ can be replaced with $u_i$ (standing for upper bound), 
	$u_i$ can be replaced with $r_i$ (standing for radius), but not sure yet
	about $p_i$.}
\begin{lemma}
\label{lem:estimateTech}
Suppose $0 \leq \gamma_k, \gamma_k' \leq 1, k \in [K]$. Let $0 \leq p_1, \ldots, p_m \leq 1$, $u_1, \ldots, u_m \geq 0$ and $w_i = \min\{p_i + u_i, 1\}, 1 \leq i \leq m$. Then
\begin{align*}
&f(A^{(m)}, w) \leq f(A^{(m)}, p) + \sum_{k=1}^{m} \gamma_k u_k,\\
&f_{\wedge}(A^{(m)}, w) \leq f_{\wedge}(A^{(m)}, p) + \sum_{k=1}^{m} (1 - \gamma_k') u_k,
\end{align*}
where $A^{(m)} = (1, 2, \ldots, m), w = (w_1, \ldots, w_m)$ and $p = (p_1, \ldots, p_m)$.
\end{lemma}
\begin{proof}
We prove this by induction. It holds obviously for $m = 1$.
\begin{align*}
&~~f(A^{(m+1)}, w)\\
&= f(A^{(m)}, w) + \gamma_{m+1}\prod_{k=1}^m(1 - w_k) w_{m+1}\\
&\leq f(A^{(m)}, w) +  \gamma_{m+1} \prod_{k=1}^m(1 - p_k) (p_{m+1} + u_{m+1})\\
&\leq f(A^{(m)}, p) + \sum_{k=1}^m \gamma_k u_k \\
&\qquad + \gamma_{m+1} \prod_{k=1}^m(1 - p_k) p_{m+1} + \gamma_{m+1} u_{m+1}\\
&= f(A^{(m+1)}, p) + \sum_{k=1}^{m+1} \gamma_k u_k
\end{align*}
\begin{align*}
&~~f_{\wedge}(A^{(m+1)}, w) \\
&= f_{\wedge}(A^{(m)}, w) -\prod_{k=1}^{m} w_k \\
&\qquad+ \gamma_{m+1}' (\prod_{k=1}^{K} w_k) (1 - w_{K+1})+ \prod_{k=1}^{K+1} w_k\\
&= f_{\wedge}(A^{(m)}, w) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} w_k) (1 - w_{m+1})\\
&\leq f_{\wedge}(A^{(m)}, w) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} p_k) (1 - w_{m+1})\\
&\leq f_{\wedge}(A^{(m)}, w) -(1 - \gamma_{m+1}') (\prod_{k=1}^{m} p_k)  (1 - p_{m+1} - u_{m+1})\\
&\leq f_{\wedge}(A^{(m)}, p) +  \sum_{k=1}^{m} (1 - \gamma_k') u_k \\
&\qquad - (1 - \gamma_{m+1}') (1 - p_{m+1}) \prod_{k=1}^{m} p_k + (1 - \gamma_{m+1}') u_{m+1}\\
&\leq f_{\wedge}(A^{(m+1)}, p) + \sum_{k=1}^{m+1} (1 - \gamma_k') u_k
\end{align*}
\end{proof}

>>>>

\wei{I do not see the purpose of putting Lemma 4.4 and 4.5 in this section. Perhaps
	they should all be moved to Section 4.3}
\shuai{I think Section 4.3 will probably be put in the appendix. So I sketch a proof of main theorem here. If all the proofs will be kept, then we don't need Lemma 4.4 and 4.5 here.}

@@

\wei{I do not understand the above paragraph and the formula below.}
\shuai{If we choose action of $\bA_t$ instead of $A_t^{\ast}$, then we can know the differece between their expected reward. But the regret is bounded by all base arms in $\bA_t$. Only the observed base arms can be estimated together. So we can only estimate the following formula. I rewrite the following formula and can explain to you later.}
\begin{align*}
&~~\EE_t[R(t, \bA_t)] \\
&= \EE[R(t, \bA_t) \bOne\{R(t, \bA_t) > 0\} \EE[(1/p_{t, \bA_t}) \bOne\{\bO_t \geq \abs{\bA_t}\}|\bA_t] | \cH_t]\\
&= \EE_t[R(t, \bA_t)(1/p_{t, \bA_t}) \bOne\{R(t, \bA_t) > 0, \bO_t \geq \abs{\bA_t}\}],\\
&~~\EE_t[R_{\wedge}(t, \bA_t)] \\
&= \EE_t[R_{\wedge}(t, \bA_t)(1/p_{\wedge, t, \bA_t}) \bOne\{R_{\wedge}(t, \bA_t) > 0, \bO_{\wedge, t} \geq \abs{\bA_t}\}].
\end{align*}

@@

The following lemma provides the relationship between an estimated mean vector and its
	upper bound, in terms of their $f$ function values.
\wei{The symbol here may need to be changed. $w_i$ coincides with weight $w_i$ before, 
		and $p$ coincides with many related probability definition using $p$.
	$w_i$ can be replaced with $u_i$ (standing for upper bound), 
	$u_i$ can be replaced with $r_i$ (standing for radius), but not sure yet
	about $p_i$.}
\shuai{Maybe we can replace $p_i$ by $w_i$ like the lemma above. I have changed accordingly.}
\begin{lemma}
\label{lem:estimateTech}
Suppose $0 \leq \gamma_k, \gamma_k' \leq 1, k \in [K]$. Let $0 \leq w_1, \ldots, w_m \leq 1$, $r_1, \ldots, r_m \geq 0$ and $u_i = \min\{w_i + r_i, 1\}, 1 \leq i \leq m$. Then
\begin{align*}
&f(A^{(m)}, u) \leq f(A^{(m)}, w) + \sum_{k=1}^{m} \gamma_k r_k,\\
&f_{\wedge}(A^{(m)}, u) \leq f_{\wedge}(A^{(m)}, w) + \sum_{k=1}^{m} (1 - \gamma_k') r_k,
\end{align*}
where $A^{(m)} = (1, 2, \ldots, m), u = (u_1, \ldots, u_m)$ and $w = (w_1, \ldots, w_m)$.
\end{lemma}
\begin{proof}
We prove this by induction. It holds obviously for $m = 1$.
\begin{align*}
&~~f(A^{(m+1)}, u)\\
&= f(A^{(m)}, u) + \gamma_{m+1}\prod_{k=1}^m(1 - u_k) u_{m+1}\\
&\leq f(A^{(m)}, u) +  \gamma_{m+1} \prod_{k=1}^m(1 - w_k) (w_{m+1} + r_{m+1})\\
&\leq f(A^{(m)}, w) + \sum_{k=1}^m \gamma_k r_k \\
&\qquad + \gamma_{m+1} \prod_{k=1}^m(1 - w_k) w_{m+1} + \gamma_{m+1} r_{m+1}\\
&= f(A^{(m+1)}, w) + \sum_{k=1}^{m+1} \gamma_k r_k
\end{align*}
\begin{align*}
&~~f_{\wedge}(A^{(m+1)}, u) \\
&= f_{\wedge}(A^{(m)}, u) -\prod_{k=1}^{m} u_k \\
&\qquad+ \gamma_{m+1}' (\prod_{k=1}^{K} u_k) (1 - u_{K+1})+ \prod_{k=1}^{K+1} u_k\\
&= f_{\wedge}(A^{(m)}, u) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} u_k) (1 - u_{m+1})\\
&\leq f_{\wedge}(A^{(m)}, u) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} w_k) (1 - u_{m+1})\\
&\leq f_{\wedge}(A^{(m)}, u) -(1 - \gamma_{m+1}') (\prod_{k=1}^{m} w_k)  (1 - w_{m+1} - r_{m+1})\\
&\leq f_{\wedge}(A^{(m)}, w) +  \sum_{k=1}^{m} (1 - \gamma_k') r_k \\
&\qquad - (1 - \gamma_{m+1}') (1 - w_{m+1}) \prod_{k=1}^{m} w_k + (1 - \gamma_{m+1}') r_{m+1}\\
&\leq f_{\wedge}(A^{(m+1)}, w) + \sum_{k=1}^{m+1} (1 - \gamma_k') r_k
\end{align*}
\end{proof}
